---
title: "Data Visualization R Project 1"
output: html_document
---

Natasha Halfin
Evan Johnston
Kaylyn Zvonek

The source functions below call the R code to reproduce the dataframes and plots we made for this project.

```{r, echo=FALSE}
library("ggplot2")
library("gplots")
library("bitops")
library("knitr")
library("plyr")
library("RCurl")
library("reshape2")

```

```{r, echo=TRUE}
source("../01 Data/dataFrames.R")
source("../02 Visualizations/ggplot_customers.R")
source("../02 Visualizations/ggplot_filterArtist.R")
source("../02 Visualizations/ggplot_filterPrice.R")
source("../02 Visualizations/ggplot_filterTitle.R")
source("../02 Visualizations/ggplot_items.R")
source("../02 Visualizations/ggplot_order_details.R")
source("../02 Visualizations/ggplot_orders.R")


```

Customer Table Dataframe

```{r, echo=TRUE}

data.frame(head(dfcustomer))
```
Order Table Dataframe
```{r, echo=TRUE}
data.frame(head(dforder))
```

Order Details Table Dataframe
```{r, echo=TRUE}
data.frame(head(dforderdetail))
```

Item Table Dataframe
```{r, echo=TRUE}
data.frame(head(dfitem))
```

Joined Table Dataframe
```{r, echo=TRUE}
data.frame(head(dfjoined))
```

*Interesting Plots*  
**Customers**
This plot depicts the number of customers by state.
```{r, echo= TRUE}
plot(customers)
```

**Order Details**
This plot indicates the quantity of types of items across orders details.
```{r, echo=TRUE}
plot(order_details)
```

**Orders**  
This plot displays the types of items ordered by each customer over a period of time.
```{r, echo=TRUE}

plot(orders)
```

**Items**
This plot shows the price distribution of items across different artists.
```{r, echo=TRUE}
plot(items)
```

**Required Plots from Joined Dataframes**
```{r, echo=TRUE}
plot(artist)
plot(price)
plot(title)


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
